\textmd{\hmwkClass:\ \hmwkTitle}\\ \small{Due\ on\ \hmwkDueDate}

### 2017-05-08 paper/main.tex

\section{Extensibility of the System}

Possible future extensions and high level explanation of how they would be
implemented (through minimal change to current system)

>>>>

\section{Extensibility of the System}
Future extensions include collisions between objects, constraints such as joints, simulating objects in three dimensions, and being able to combine objects into larger systems of objects. Collisions and other kinds of constraints could be implemented by adding an interaction that produces forces that enforce these constraints. Objects could be simulated in three dimensions by defining three dimensional object types and using the generic arithmetic to operate on higher dimensional vectors. Objects could be combined into larger systems using procedures, if there is a way to link them together, for example by constraints.
